Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data

### 2011-05-05 ltx/data_paper/DataPaper.tex

where $e_t(\mathbf{r}) = \sigma_W[W\left( \mathbf{r},t+T_s \right)-W\left( \mathbf{r},t \right)]$ is the increment of a space-time Wiener process, $i.i.d.$ with zero spatial mean such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,T_s\sigma_W^2\gamma(\mathbf{r}-\mathbf{r}'))$. Here $\mathcal{GP}(\mathbf 0,T_s\sigma_W^2\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.

>>>>

where $e_t(\mathbf{r}) = \sigma_W[W\left( \mathbf{r},t+T_s \right)-W\left( \mathbf{r},t \right)]$ is the increment of a space-time Wiener process, $i.i.d.$ with zero spatial mean such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\sigma_d^2\gamma(\mathbf{r}-\mathbf{r}'))$, where $\sigma_d^2=T_s\sigma_W^2$. Here $\mathcal{GP}(\mathbf 0,\sigma_d^2\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
